\section{System's Perspective}
\subsection{Design and Architecture}
\subsection{Dependencies}

The following are the dependencies for our Minitwit system, listed in an orgainized manner in order to better provide an overview.

\textbf{Runtime Dependencies}

These dependencies include the environment to run the application on including the operating system, VM technologies and programming language.

\begin{itemize}
    \item Ubuntu Linux: Operating System
    \item Docker (swarm mode): Virtual Machine
    \item golang:1.25 (Docker image)
\end{itemize}

\textbf{Application Libraries}

This list contains the libraries and what each library is for.

\begin{itemize}
    \item Go 1.25.6: Programming language.
    \item Gorilla Mux: HTTP request routing.
    \item Gorilla Sessions: Session management.
    \item GORM: Object-relational mapper.
    \item PostgreSQL Driver: Database connectivity.
    \item go-sqlite3: SQLite support for testing/development.
    \item Zerolog: Structured logging.
    \item Prometheus client\_golang: Metrics instrumentation.
\end{itemize}

\textbf{Testing}

\begin{itemize}
    \item Python 3.11: Programming language
    \item pytest: Testing framework
    
\end{itemize}

\textbf{DevOps / Build Dependencies}

This list includes tools for employing DevOps practices. 

\begin{itemize}
    \item Github: Code repository
    \item Dockerhub: Docker image repository
    \item Github Actions: CI/CD Pipeline
    \item Codacy: Quality assurance
    \item SonarQube: Quality assurance
\end{itemize}

\subsection{Current System State}